---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

### Read and convert data set to class gpm
```{r, fig.show='hold'}
data(abies_alba)

abies_alba <- abies_alba[complete.cases(abies_alba),]

meta <- createGPMMeta(dataset = abies_alba, 
                      selector = 1, response = c(6:8), 
                      independent = c(16:247), meta = c(2:5, 9:15))
alb <- gpm(abies_alba, meta)
```



```{r, fig.show='hold'}
# source("http://bioconductor.org/biocLite.R")
# biocLite("impute")
# library(impute)

```


```{r, fig.show='hold'}
alb_resamples <- resamplingsByVariable(x = alb@data$input, 
                                       selector = alb@data$input$ID, 
                                       resample = 5)


alb_trte <- splitMultResp(x = alb@data$input, 
                          response = alb@meta$input$RESPONSE,
                          resamples = alb_resamples,
                          p = 0.75)

response <- alb@meta$input$RESPONSE
independent <- alb@meta$input$INDEPENDENT

models <- trainModel(x = alb@data$input, 
                     response = response, independent = independent,
                     resamples = alb_trte, n_var = seq(10,200,100),
                     response_nbr = c(1), resample_nbr = c(2))

```



















Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` setion of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
