---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
head(iris)

meta <- createGPMMeta(iris, type = "input",
                      selector = NULL, response = 5, 
                      independent = c(1:4), meta = NULL)
iris_gpm <- gpm(iris, meta, scale = TRUE)


iris_resamples <- resamplingsByVariable(x = iris_gpm@data$input, 
                                        resample = 10, 
                                        use_selector = "FALSE")

iris_trte <- splitMultResp(x = iris_gpm@data$input, 
                           response = iris_gpm@meta$input$RESPONSE,
                           resamples = iris_resamples,
                           p = 0.80)


models <- trainModel(x = iris_gpm,
                     response = iris_gpm@meta$input$RESPONSE, 
                     independent = iris_gpm@meta$input$INDEPENDENT,
                     resamples = iris_trte, 
                     n_var = c(seq(length(iris_gpm@meta$input$INDEPENDENT))),
                     mthd = "rf", 
                     seed_nbr = 2016, 
                     cv_nbr = 5,
                     var_selection = "sd",
                     filepath_tmp = NULL)

var_imp <- compVarImp(models, scale = FALSE)

var_imp_scale <- compVarImp(models, scale = TRUE)

var_imp_plot <- plotVarImp(var_imp)

var_imp_heat <- plotVarImpHeatmap(var_imp_scale, xlab = "Species", ylab = "Band")

tstat <- compContTests(models, mean = TRUE)
```


Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
