---
title: "GPM example using iris data"
author: "Thomas Nauss"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
The following gives a short overview on how to use GPM for prediction. For this
example, the iris dataset is used.
```{r, warning=FALSE, message=FALSE, results="hide"}
library(gpm)
head(iris)
```

First, the gpm object is created by defining meta information and then adding
the dataset and the corresponding meta information to the gpm class.
```{r}
meta <- createGPMMeta(iris, type = "input",
                      selector = NULL, response = 5, 
                      predictor = c(1:4), meta = NULL)
iris_gpm <- gpm(iris, meta, scale = TRUE)
```

Once the gpm object has been created, it can be used as input for computing
resamples and splitting the resamples into test and training datasets afterwards.
```{r}
iris_resamples <- resamplingsByVariable(x = iris_gpm@data$input, 
                                        resample = 20, 
                                        use_selector = "FALSE")

iris_trte <- splitMultResp(x = iris_gpm@data$input, 
                           response = iris_gpm@meta$input$RESPONSE,
                           resamples = iris_resamples,
                           p = 0.90)
```

Once the resampling has been defined, the model tuning and feature selection is
handeld by the ``trainModel`` function.
```{r, message=FALSE}
models <- trainModel(x = iris_gpm,
                     response = iris_gpm@meta$input$RESPONSE, 
                     independent = iris_gpm@meta$input$INDEPENDENT,
                     resamples = iris_trte, 
                     n_var = c(seq(length(iris_gpm@meta$input$INDEPENDENT))),
                     mthd = "rf", 
                     seed_nbr = 1, 
                     cv_nbr = 5,
                     var_selection = "indv",
                     filepath_tmp = NULL)
```

Since some information related to the model and its performance is commonly
required, the following functions compute the unscaled or scaled importance of
the individual explanatory (i.e. independent) varialbes. Only those variables are
considered, which have been included at least once into a final model.
```{r}
var_imp <- compVarImp(models, scale = FALSE)
var_imp_scale <- compVarImp(models, scale = TRUE)

```

The statistics can further be used to create some plots.
```{r, fig.show='hold'}
plotVarImp(var_imp)

plotVarImpHeatmap(var_imp_scale, xlab = "Species", ylab = "Band")

```

Finally, performance statistics can be computed for regression or - as in this example - classification models.
```{r}
tstat <- compContTests(models, mean = TRUE)
summary(tstat[[2]])
```


```{r}
obb <- unlist(lapply(models[[1]], function(x){x$model$fit$err.rate[x$model$fit$ntree,1]}))
kappa_int <- unlist(lapply(models[[1]], function(x){helpCalcKappa(x$model$fit$confusion)}))
kappa_int <- kappa_int[names(kappa_int) == "Kappa"]

summary(kappa_int)
summary(tstat[[2]]$Kappa)
summary(obb)

boxplot(kappa_int, tstat[[2]]$Kappa, (1-obb),
        names = c("Kappa internal", "Kappa CV", "OBB"),
        sub=("20-fold sampling of iris data with a 50:50 training to test ratio."))
```

