---
title: "IPS"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

### Read and clean data set
```{r, fig.show='hold'}
data(ips_clean)
# fix(input)
# rename NC for missing data as NA
ips <- ips_clean
# ips <- as.data.frame(apply(ips, 2, function(x) gsub("-/-",NA,x)))
# 
# ips$daYN <- "yes" # a
# ips$daYN[ips$da == "d"] <- "no" # d
# ips$daYN <- as.factor(ips$daYN)

str(ips)
```


### Convert data set to class gpm
```{r, fig.show='hold'}
meta <- createGPMMeta(dataset = ips, 
                      selector = 1, response = c(2), 
                      independent = c(5:3038), meta = NULL)
ips <- gpm(ips, meta)
```


### Compile model evaluation dataset
```{r, fig.show='hold'}
summary(ips@data$input$daYN)

ips_resamples <- resamplingsByVariable(x = ips@data$input, 
                                       selector = as.character(unlist(ips@data$input[ips@meta$input$RESPONSE])), grabs = 20, 
                                       resample = 10)

ips_trte <- splitMultResp(x = ips@data$input, 
                          p = 0.75,
                          response = ips@meta$input$RESPONSE,
                          resamples = ips_resamples)
```


```{r, fig.show='hold'}
response <- ips@meta$input$RESPONSE
independent <- ips@meta$input$INDEPENDENT

models <- trainModel(x = ips@data$input, 
                     response = response, 
                     independent = independent,
                     resamples = ips_trte, 
                     n_var = seq(5,200,20))

var_imp <- compVarImp(models)

var_imp_plot <- plotVarImp(var_imp)

var_imp_heat <- plotVarImpHeatmap(var_imp, xlab = "Species", ylab = "Band")

tests <- compContTests(models)

tstat_mean <- lapply(tests, function(x){
  data.frame(RESPONSE = x$RESPONSE[1], 
             KAPPA_MEAN = mean(x$Kappa, na.rm = TRUE),
             POD_MEAN = mean(x$POD, na.rm = TRUE),
             FAR_MEAN = mean(x$FAR, na.rm = TRUE), 
             POFD_MEAN = mean(x$POFD, na.rm = TRUE),
             ACCURACY_MEAN = mean(x$ACCURACY, na.rm = TRUE),
             SR_MEAN = mean(x$SR, na.rm = TRUE),
             TS_MEAN = mean(x$TS, na.rm = TRUE),
             ETS_MEAN = mean(x$ETS, na.rm = TRUE),
             HK_MEAN = mean(x$HK, na.rm = TRUE))
})
tstat_mean <- do.call("rbind", tstat_mean)
tstat_mean <- merge(tstat_mean, prevalence, by = "RESPONSE")
tstat_mean[order(tstat_mean$KAPPA_MEAN, decreasing = TRUE),]
corrplot(cor(tstat_mean[, -1]))

```



















Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` setion of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
